---
dataMaid: yes
title: DDS Analytics Codebook 
date: 2019-04-13
output: 
  html_document:
    keep_md: TRUE
  
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```
```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations       1470

Number of variables            35
---------------------------------




# Codebook summary table

--------------------------------------------------------------------
  Variable            Class         # unique  Missing  Description  
                                      values                        
--------------------- ----------- ---------- --------- -------------
  **[Age]**           numeric             43  0.00 %   Employee Age            
  
  **[Attrition]**     numeric              2  0.00 %   Attrition              
  
  **[Travel]**        numeric              3  0.00 %   Business Travel              
  
  **[DailyRate]**     numeric            886  0.00 %   Daily Rate             
  
  **[Department]**    numeric              3  0.00 %   Department             
  
  **[DisFromHome]**   numeric             29  0.00 %   Distance From Home             
  
  **[Education]**     numeric              5  0.00 %   Education Level              
  
  **[EduField]**      numeric              6  0.00 %   Field of Education             
  
  **[EmpCount]**      numeric              1  0.00 %   Employee Count              
  
  **[EmployeeID]**    numeric           1470  0.00 %   Employee ID             
  
  **[EnvSatis]**      numeric              4  0.00 %   Environmental Satisfaction             
  
  **[Gender]**        numeric              2  0.00 %   Gender             
  
  **[HourlyRate]**    numeric             71  0.00 %   Hourly Rate             
  
  **[JobInvolve]**    numeric              4  0.00 %   Job Involvement             
  
  **[JobLevel]**      numeric              5  0.00 %   Job Level              
  
  **[JobRole]**       numeric              9  0.00 %   Job Role              
  
  **[JobSatis]**      numeric              4  0.00 %   Job Satisfaction             
  
  **[MaritalStat]**   numeric              3  0.00 %   Marital Status             
  
  **[MonIncome]**     numeric           1349  0.00 %   Monthly Income             
  
  **[MonthlyRate]**   numeric           1427  0.00 %   Monthly Rate             
  
  **[NumCoWork]**     numeric             10  0.00 %   Number of Companies Worked             
  
  **[Over18]**        character            1  0.00 %   Over Age 18              
  
  **[OverTime]**      numeric              2  0.00 %   OverTime             
  
  **[SalaryIncr]**    numeric             15  0.00 %   Percent Salary Hike             
  
  **[PerformRate]**   numeric              2  0.00 %   Performance Rate             
  
  **[RelateSatis]**   numeric              4  0.00 %   Relationship Satisfaction             
  
  **[StdHours]**      numeric              1  0.00 %   Standard Hours             
  
  **[StockOption]**   numeric              4  0.00 %   Stock Option Level             
  
  **[NumWorkYear]**   numeric             40  0.00 %   Total Working Years              
  
  **[TrainTime]**     numeric              7  0.00 %   Training Times Last Year             
  
  **[WorkLifeBal]**   numeric              4  0.00 %   Work/Life Balance              
  
  **[YearsAtCo]**     numeric             37  0.00 %   Years at Company             
  
  **[DuraCurRole]**   numeric             19  0.00 %   Years in Current Role              
  
  **[LastPromote]**   numeric             16  0.00 %   Years since Last Promotion             
  
  **[CurManage]**     numeric             18  0.00 %   Years with Current Manager             
--------------------------------------------------------------------




# Variable list
## Age

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          43

Median                           36

1st and 3rd quartiles        30; 43

Min. and max.                18; 60
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-1-Age', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(15L, 20L, 25L, 30L, 
35L, 40L, 45L, 50L, 55L), xmax = c(20L, 25L, 30L, 35L, 40L, 45L, 
50L, 55L, 60L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(28L, 
95L, 263L, 343L, 276L, 192L, 130L, 96L, 47L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Age")
```
</div>
</div>




---

## Attrition

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Median                            0

1st and 3rd quartiles          0; 0

Min. and max.                  0; 1
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-Attrition', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.1, 0.2, 0.3, 0.4, 
0.5, 0.6, 0.7, 0.8, 0.9), xmax = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 
0.7, 0.8, 0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1233L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 237L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Attrition")
```
</div>
</div>




---

## Travel

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           3

Median                            2

1st and 3rd quartiles          2; 2

Min. and max.                  1; 3
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-Travel', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8), xmax = c(1.2, 1.4, 1.6, 1.8, 2, 2.2, 
2.4, 2.6, 2.8, 3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(150L, 
0L, 0L, 0L, 1043L, 0L, 0L, 0L, 0L, 277L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Travel")
```
</div>
</div>




---

## DailyRate

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values           886

Median                            802

1st and 3rd quartiles       465; 1157

Min. and max.               102; 1499
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-DailyRate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(100L, 200L, 300L, 400L, 
500L, 600L, 700L, 800L, 900L, 1000L, 1100L, 1200L, 1300L, 1400L
), xmax = c(200L, 300L, 400L, 500L, 600L, 700L, 800L, 900L, 1000L, 
1100L, 1200L, 1300L, 1400L, 1500L), ymin = c(0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(106L, 91L, 103L, 105L, 123L, 
119L, 86L, 107L, 107L, 90L, 111L, 105L, 123L, 94L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "DailyRate")
```
</div>
</div>




---

## Department

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           3

Median                            2

1st and 3rd quartiles          2; 3

Min. and max.                  1; 3
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-Department', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8), xmax = c(1.2, 1.4, 1.6, 1.8, 2, 2.2, 
2.4, 2.6, 2.8, 3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(63L, 
0L, 0L, 0L, 961L, 0L, 0L, 0L, 0L, 446L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Department")
```
</div>
</div>




---

## DisFromHome

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          29

Median                            7

1st and 3rd quartiles         2; 14

Min. and max.                 1; 29
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-6-DisFromHome', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(419L, 148L, 124L, 164L, 
171L, 49L, 40L, 58L, 46L, 47L, 37L, 55L, 50L, 35L, 27L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "DisFromHome")
```
</div>
</div>




---

## Education

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           5

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 5
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-Education', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(170L, 282L, 0L, 572L, 0L, 398L, 
0L, 48L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "Education")
```
</div>
</div>




---

## EduField

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           6

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 6
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-8-EduField', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5, 5, 5.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 
6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(27L, 606L, 
0L, 159L, 0L, 464L, 0L, 82L, 0L, 132L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "EduField")
```
</div>
</div>




---

## EmpCount

* The variable only takes one (non-missing) value: \"1\". The variable contains 0 \% missing observations.



---

## EmployeeID

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.              0 (0 %)

Number of unique values                1470

Median                               1020.5

1st and 3rd quartiles       491.25; 1555.75

Min. and max.                       1; 2068
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-10-EmployeeID', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 200, 400, 600, 800, 
1000, 1200, 1400, 1600, 1800, 2000), xmax = c(200, 400, 600, 
800, 1000, 1200, 1400, 1600, 1800, 2000, 2200), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(149L, 144L, 155L, 129L, 
140L, 141L, 136L, 140L, 151L, 137L, 48L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "EmployeeID")
```
</div>
</div>




---

## EnvSatis

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-11-EnvSatis', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(284L, 
0L, 0L, 0L, 287L, 0L, 0L, 0L, 0L, 453L, 0L, 0L, 0L, 0L, 446L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "EnvSatis")
```
</div>
</div>




---

## Gender

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Median                            1

1st and 3rd quartiles          0; 1

Min. and max.                  0; 1
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-12-Gender', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.1, 0.2, 0.3, 0.4, 
0.5, 0.6, 0.7, 0.8, 0.9), xmax = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 
0.7, 0.8, 0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(588L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 882L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Gender")
```
</div>
</div>




---

## HourlyRate

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values            71

Median                             66

1st and 3rd quartiles       48; 83.75

Min. and max.                 30; 100
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-13-HourlyRate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(30L, 35L, 40L, 45L, 
50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L), xmax = c(35L, 
40L, 45L, 50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L, 100L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(107L, 
84L, 115L, 103L, 104L, 114L, 97L, 93L, 107L, 111L, 113L, 103L, 
104L, 115L)), class = "data.frame", row.names = c(NA, -14L)), 
    vnam = "HourlyRate")
```
</div>
</div>




---

## JobInvolve

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-14-JobInvolve', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(83L, 
0L, 0L, 0L, 375L, 0L, 0L, 0L, 0L, 868L, 0L, 0L, 0L, 0L, 144L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "JobInvolve")
```
</div>
</div>




---

## JobLevel

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           5

Median                            2

1st and 3rd quartiles          1; 3

Min. and max.                  1; 5
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-15-JobLevel', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(543L, 534L, 0L, 218L, 0L, 106L, 
0L, 69L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "JobLevel")
```
</div>
</div>




---

## JobRole

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           9

Median                            6

1st and 3rd quartiles          3; 8

Min. and max.                  0; 9
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-16-JobRole', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 9), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(52L, 131L, 259L, 102L, 145L, 80L, 
292L, 326L, 83L)), class = "data.frame", row.names = c(NA, -9L
)), vnam = "JobRole")
```
</div>
</div>




---

## JobSatis

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-17-JobSatis', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(289L, 
0L, 0L, 0L, 280L, 0L, 0L, 0L, 0L, 442L, 0L, 0L, 0L, 0L, 459L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "JobSatis")
```
</div>
</div>




---

## MaritalStat

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           3

Median                            2

1st and 3rd quartiles          1; 2

Min. and max.                  1; 3
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-18-MaritalStat', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8), xmax = c(1.2, 1.4, 1.6, 1.8, 2, 2.2, 
2.4, 2.6, 2.8, 3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(470L, 
0L, 0L, 0L, 673L, 0L, 0L, 0L, 0L, 327L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "MaritalStat")
```
</div>
</div>




---

## MonIncome

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1349

Median                             4919

1st and 3rd quartiles        2911; 8379

Min. and max.               1009; 19999
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-19-MonIncome', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2000, 4000, 6000, 
8000, 10000, 12000, 14000, 16000, 18000), xmax = c(2000, 4000, 
6000, 8000, 10000, 12000, 14000, 16000, 18000, 20000), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(33L, 510L, 371L, 175L, 100L, 
86L, 53L, 16L, 57L, 69L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "MonIncome")
```
</div>
</div>




---

## MonthlyRate

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values              1427

Median                            14235.5

1st and 3rd quartiles       8047; 20461.5

Min. and max.                 2094; 26999
-----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-20-MonthlyRate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(2000L, 4000L, 6000L, 
8000L, 10000L, 12000L, 14000L, 16000L, 18000L, 20000L, 22000L, 
24000L, 26000L), xmax = c(4000L, 6000L, 8000L, 10000L, 12000L, 
14000L, 16000L, 18000L, 20000L, 22000L, 24000L, 26000L, 28000L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(110L, 
130L, 123L, 124L, 118L, 116L, 114L, 120L, 117L, 119L, 131L, 99L, 
49L)), class = "data.frame", row.names = c(NA, -13L)), vnam = "MonthlyRate")
```
</div>
</div>




---

## NumCoWork

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          10

Median                            2

1st and 3rd quartiles          1; 4

Min. and max.                  0; 9
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-21-NumCoWork', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 9), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(718L, 146L, 159L, 139L, 63L, 70L, 
74L, 49L, 52L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "NumCoWork")
```
</div>
</div>




---

## Over18

* The variable only takes one (non-missing) value: \"Y\". The variable contains 0 \% missing observations.



---

## OverTime

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Median                            0

1st and 3rd quartiles          0; 1

Min. and max.                  0; 1
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-23-OverTime', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.1, 0.2, 0.3, 0.4, 
0.5, 0.6, 0.7, 0.8, 0.9), xmax = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 
0.7, 0.8, 0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1054L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 416L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "OverTime")
```
</div>
</div>




---

## SalaryIncr

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          15

Median                           14

1st and 3rd quartiles        12; 18

Min. and max.                11; 25
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-24-SalaryIncr', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = 11:24, xmax = 12:25, ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(408L, 209L, 
201L, 101L, 78L, 82L, 89L, 76L, 55L, 48L, 56L, 28L, 21L, 18L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "SalaryIncr")
```
</div>
</div>




---

## PerformRate

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Median                            3

1st and 3rd quartiles          3; 3

Min. and max.                  3; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-25-PerformRate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(3, 3.1, 3.2, 3.3, 3.4, 
3.5, 3.6, 3.7, 3.8, 3.9), xmax = c(3.1, 3.2, 3.3, 3.4, 3.5, 3.6, 
3.7, 3.8, 3.9, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1244L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 226L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "PerformRate")
```
</div>
</div>




---

## RelateSatis

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-26-RelateSatis', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(276L, 
0L, 0L, 0L, 303L, 0L, 0L, 0L, 0L, 459L, 0L, 0L, 0L, 0L, 432L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "RelateSatis")
```
</div>
</div>




---

## StdHours

* The variable only takes one (non-missing) value: \"80\". The variable contains 0 \% missing observations.



---

## StockOption

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            1

1st and 3rd quartiles          0; 1

Min. and max.                  0; 3
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-28-StockOption', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8), xmax = c(0.2, 
0.4, 0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 
3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(631L, 
0L, 0L, 0L, 596L, 0L, 0L, 0L, 0L, 158L, 0L, 0L, 0L, 0L, 85L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "StockOption")
```
</div>
</div>




---

## NumWorkYear

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          40

Median                           10

1st and 3rd quartiles         6; 15

Min. and max.                 0; 40
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-29-NumWorkYear', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35), xmax = c(5, 10, 15, 20, 25, 30, 35, 40), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(316L, 607L, 191L, 149L, 109L, 
52L, 33L, 13L)), class = "data.frame", row.names = c(NA, -8L)), 
    vnam = "NumWorkYear")
```
</div>
</div>




---

## TrainTime

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           7

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  0; 6
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-30-TrainTime', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5, 4, 4.5, 5, 5.5), xmax = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5, 5, 5.5, 6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(54L, 71L, 0L, 547L, 0L, 491L, 0L, 123L, 0L, 119L, 
0L, 65L)), class = "data.frame", row.names = c(NA, -12L)), vnam = "TrainTime")
```
</div>
</div>




---

## WorkLifeBal

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-31-WorkLifeBal', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(80L, 
0L, 0L, 0L, 344L, 0L, 0L, 0L, 0L, 893L, 0L, 0L, 0L, 0L, 153L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "WorkLifeBal")
```
</div>
</div>




---

## YearsAtCo

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          37

Median                            5

1st and 3rd quartiles          3; 9

Min. and max.                 0; 40
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-32-YearsAtCo', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35), xmax = c(5, 10, 15, 20, 25, 30, 35, 40), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(776L, 448L, 108L, 72L, 41L, 9L, 
12L, 4L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "YearsAtCo")
```
</div>
</div>




---

## DuraCurRole

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          19

Median                            3

1st and 3rd quartiles          2; 7

Min. and max.                 0; 18
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-33-DuraCurRole', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(673L, 239L, 73L, 311L, 96L, 
32L, 25L, 15L, 6L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "DuraCurRole")
```
</div>
</div>




---

## LastPromote

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          16

Median                            1

1st and 3rd quartiles          0; 3

Min. and max.                 0; 15
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-34-LastPromote', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8, 9, 10, 11, 12, 13, 14), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 
9, 10, 11, 12, 13, 14, 15), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(938L, 159L, 52L, 61L, 45L, 32L, 
76L, 18L, 17L, 6L, 24L, 10L, 10L, 9L, 13L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "LastPromote")
```
</div>
</div>




---

## CurManage

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          18

Median                            3

1st and 3rd quartiles          2; 7

Min. and max.                 0; 17
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-35-CurManage', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(683L, 240L, 60L, 323L, 91L, 
40L, 19L, 7L, 7L)), class = "data.frame", row.names = c(NA, -9L
)), vnam = "CurManage")
```
</div>
</div>




---



Report generation information:

 *  Created by Richard Hart (username: `Richard`).

 *  Report creation time: Sat Apr 13 2019 15:55:26

 *  Report was run from directory: `D:/Dropbox/Git_Projects/DDS6306_CaseStudy02`

 *  dataMaid v1.2.0 [Pkg: 2018-10-03 from CRAN (R 3.5.3)]

 *  R version 3.5.2 (2018-12-20).

 *  Platform: x86_64-w64-mingw32/x64 (64-bit)(Windows >= 8 x64 (build 9200)).

 *  Function call: `makeDataReport(data = hr, mode = c("summarize", "visualize", 
"check"), smartNum = FALSE, file = "codebook_hr.Rmd", checks = list(
    character = "showAllFactorLevels", factor = "showAllFactorLevels", 
    labelled = "showAllFactorLevels", haven_labelled = "showAllFactorLevels", 
    numeric = NULL, integer = NULL, logical = NULL, Date = NULL), 
    listChecks = FALSE, maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for hr")`

