---
title: "CaseStudy2_R_Code"
author: "AMarkum"
date: "4/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This file contains base code for data exploration

# Packages required for this project
```{r packages, include=TRUE}
library(ggplot2)
library(psych)
library(lattice)
library(corrplot)
library(vcd)
```

# load your raw data
```{r loadData, include=TRUE}
att.df <- read.csv(paste("CaseStudy2-singlesheet.csv", sep = ""))
names(att.df)[1]<- "Age"
attach(att.df)
str(att.df)
```

# Split the data into a training and testing set. The training set is used to fit the model
```{r train_test, include=TRUE}
train <- att.df[1:799,]
test<-att.df[800:1400,]
model <- glm(Attrition ~ Age+BusinessTravel+Department+DistanceFromHome+
               Education+EducationField+EnvironmentSatisfaction+Gender+JobInvolvement+
               JobLevel+JobRole+JobSatisfaction+MaritalStatus+MonthlyIncome+NumCompaniesWorked+
               OverTime+PercentSalaryHike+PerformanceRating+RelationshipSatisfaction+
               TotalWorkingYears+TrainingTimesLastYear+WorkLifeBalance+ 
               YearsAtCompany+YearsInCurrentRole+YearsSinceLastPromotion+
               YearsWithCurrManager,family=binomial(link='logit'),data=train)
summary(model)
```

# Next step is to run the anova
```{r anova, include=TRUE}
anova(model, test="Chisq")
str(att.df)
```

# Exploratory Data Analysis
```{r explore, include=TRUE}
describe(att.df)

table(Attrition)

table(BusinessTravel)

table(EducationField)

table(Education)

table(EnvironmentSatisfaction)

table(Gender)

table(JobInvolvement)

table(JobRole)

table(JobLevel)

table(JobSatisfaction)

table(MaritalStatus)

table(OverTime)
```

# Let's do some comparisons
```{r tables, include=TRUE}
mytable_performance<- xtabs(~PerformanceRating+Attrition, data=att.df)
round(prop.table(mytable_performance,1)*100,2)

mytable_overtime<- xtabs(~OverTime+Attrition, data=att.df)
round(prop.table(mytable_overtime,1)*100,2)

mytable_worklifebalance<- xtabs(~WorkLifeBalance+Attrition, data=att.df)
round(prop.table(mytable_worklifebalance,1)*100,2)

mytable_jobrole<- xtabs(~JobRole+Attrition, data=att.df)
round(prop.table(mytable_jobrole,1)*100,2)

mytable_numcompaniesworked<- xtabs(~NumCompaniesWorked+Attrition, data=att.df)
round(prop.table(mytable_numcompaniesworked,1)*100,2)

mytable_maritalstatus<- xtabs(~MaritalStatus+Attrition, data=att.df)
round(prop.table(mytable_maritalstatus,1)*100,2)

mytable_gender<- xtabs(~Gender+Attrition, data=att.df)
round(prop.table(mytable_gender,1)*100,2)

mytable_environmentsatisfaction<- xtabs(~EnvironmentSatisfaction+Attrition, data=att.df)
round(prop.table(mytable_environmentsatisfaction,1)*100,2)

mytable_businesstravel<- xtabs(~BusinessTravel+Attrition, data=att.df)
round(prop.table(mytable_businesstravel,1)*100,2)

mytable_educationfield<- xtabs(~EducationField+Attrition, data=att.df)
round(prop.table(mytable_educationfield,1)*100,2)

mytable_jobsatisfaction<- xtabs(~JobSatisfaction+Attrition, data=att.df)
round(prop.table(mytable_jobsatisfaction,1)*100,2)

mytable_education<- xtabs(~Education+Attrition, data=att.df)
round(prop.table(mytable_education,1)*100,2)
```

# Visualize the data for ease in understanding
```{r boxplots_histograms, include=TRUE}
boxplot(Age~Attrition, main="Boxplot", xlab="Age", ylab="Attrition(Yes/No)",
        horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(DistanceFromHome~Attrition, main="Boxplot", xlab="Distance from Home",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(MonthlyIncome~Attrition, main="Boxplot", xlab="MonthlyIncome",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(YearsWithCurrManager~Attrition, main="Boxplot", xlab="Years with Current Manager",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(MonthlyRate~Attrition, main="Boxplot", xlab="Monthly Rate",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(DailyRate~Attrition, main="Boxplot", xlab="Daily Rate",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

boxplot(HourlyRate~Attrition, main="Boxplot", xlab="Hourly Rate",
        ylab="Attrition(Yes/No)", horizontal=TRUE, col=c("pink", "lightblue"))

hist(Age,xlab="Age", ylab="count", breaks=20, main="Organization's Age Variability",
     col="lightblue", freq=FALSE)

hist(MonthlyIncome,xlab="Monthly Income", ylab="count", breaks=20, main="Income Distribution",
     col="lightblue", freq=FALSE)

hist(YearsAtCompany,xlab="Years with the Company", ylab="count", breaks=20, main="Employee Longevity",
     col="lightblue", freq=FALSE)

hist(YearsWithCurrManager,xlab="Years with Curent Manager", ylab="count", breaks=20,
     main="Length of Employee/Manager Relationship", col="lightblue", freq=FALSE)

hist(PercentSalaryHike,xlab="Salary Hike %", ylab="count", breaks=20,
     main="Employee Pay Increases", col="lightblue", freq=FALSE)
```

# A different view of things...
```{r histograms, include=TRUE}
histogram(~Attrition | JobRole)

histogram(~Attrition | Department, layout=c(4,1), col=c("lightblue", "pink"))

histogram(~PercentSalaryHike | Attrition)

histogram(~Education | Attrition)
```

# Find our correlations and create a visualization
```{r correlations, include=TRUE}
round (cor(att.df[, c(1,4,6,7,11,13,14,15,17,19,20,21,24,25,26,29:35)]),2)

corrplot(corr=cor(att.df[,c(1,4,6,7,11,13,14,15,17,19,20,21,24,25,26,29:35)],
                  use="complete.obs"),method="ellipse")
```

#Check the hypothesis test regarding whether there is a significant difference
#in the average monthly income of Employees who leave vs. those who stay
```{r transformIncome, include=TRUE}
log.trans.Income = log(MonthlyIncome)
t.test(log.trans.Income~Attrition, var.equal=TRUE)
```

#Check the hypothesis test regarding whether there is a significant difference
#in the average monthy rate between Employees who leave vs. those who stay
```{r transformRate, include=TRUE}
log.trans.Rate = log(MonthlyRate)
t.test(log.trans.Rate~Attrition,var.equal=TRUE)
```

#Check the hypothesis test regarding whether there is a significant difference
#in the average daily rate between Employees who leave vs. those who stay
```{r transformDailyRate, include=TRUE}
log.trans.DailyRate = log(DailyRate)
t.test(log.trans.DailyRate~Attrition,var.equal=TRUE)
```

#Conduct a Chi-square test of the impact of Business Travel on Attrition
```{r ChiSQTravel, include=TRUE}
ChiSq_table_businesstravel <- xtabs(~BusinessTravel+Attrition, data=att.df)
round(prop.table(ChiSq_table_businesstravel,1)*100,2)
chisq.test(ChiSq_table_businesstravel)
```

#Conducting a Chi-square test of the impact of Job Satisfaction on Attrition
```{r ChiSQJobSatisfaction, include=TRUE}
ChiSq_table_jobsatisfaction <- xtabs(~JobSatisfaction+Attrition, data=att.df)
round(prop.table(ChiSq_table_jobsatisfaction,1)*100,2)
chisq.test(ChiSq_table_jobsatisfaction)
```

#Alternately, you can conduct a Fisher's Exact Test for Count Data instead of
#the Chi-square test
```{r FisherTest, include=TRUE}
fisher.test(mytable_jobsatisfaction)
assocstats(mytable_jobsatisfaction)
```