---
author: "Andy Nguyen, Amy Markum, Richard Hart, Tom Gianelle"
date: "March 28, 2019"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(readxl)
library(tidyquant)
library(pastecs)
library(ggplot2)
library(corrplot)
library(MASS)
library(rpart.plot)
library(ROSE)
library(randomForest)
library(caret)

```

``` {r SessionInfo}
sessionInfo()
```

# Introduction
All organizations experience attrtion through the normal course of business. Natural attrition occurs in many ways, such as retirement, resignation, and termination of individual employees, or through downsizing or restructuring of the company. However, organizations should keep an eye on attrition to ensure they retain experienced talent and don't waste resources replacing good employees. Additionally, attrition can act as a barometer for the organization's overall health and corporate culture.
So how does the organization know whether its turnover rate is "good" or "bad"? What should the organization's target attrition rate be? To answer that question, the organization needs know two things: 1) What is the organization's current turnover rate, and 2) What is the average turnover rate for the industry.

### 2A. Clean Raw Data

``` {r 2a}
require(readxl)
Employee_rawdata <- as.data.frame(read_excel("Data/CaseStudy2-data.xlsx"))
dim(Employee_rawdata)
emp <- Employee_rawdata
```
  * There are 1470 rows and 35 columns in the employee raw data frame.

### 2B

``` {r 2b, include = FALSE, echo = FALSE}
for (i in 1:ncol(Employee_rawdata)) {
  if (nchar(colnames(Employee_rawdata)[i]) > 12) {
    print(colnames(Employee_rawdata)[i])
    print(i)
  }
}
# BusinessTravel shortened to Travel
colnames(Employee_rawdata)[3] <- "Travel"
# DistanceFromHome shortened to DisFromHome
colnames(Employee_rawdata)[6] <- "DisFromHome"
# EducationField shortened to EduField
colnames(Employee_rawdata)[8] <- "EduField"
# EmployeeCount shortened to EmpCount
colnames(Employee_rawdata)[9] <- "EmpCount"
# EmployeeNumber shortened to EmployeeID
colnames(Employee_rawdata)[10] <- "EmployeeID"
# EnvironmentSatisfaction shortened to EnvSatis
colnames(Employee_rawdata)[11] <- "EnvSatis"
# JobInvolvement shortened to JobInvolve
colnames(Employee_rawdata)[14] <- "JobInvolve"
# JobSatisfaction shortened to JobSatis
colnames(Employee_rawdata)[17] <- "JobSatis"
# MaritalStatus shortened to MaritalStat
colnames(Employee_rawdata)[18] <- "MaritalStat"
# MonthlyIncome shortened to MonIncome
colnames(Employee_rawdata)[19] <- "MonIncome"
# NumCompaniesWorked shortened to NumCoWork
colnames(Employee_rawdata)[21] <- "NumCoWork"
# PercentSalaryHike shortened to SalaryIncr.
colnames(Employee_rawdata)[24] <- "SalaryIncr"
# PerfomanceRating shortened to PerformRate
colnames(Employee_rawdata)[25] <- "PerformRate"
# RelationshipSatisfaction shortened to RelateSatis
colnames(Employee_rawdata)[26] <- "RelateSatis"
# StandardHours shortened to StdHours
colnames(Employee_rawdata)[27] <- "StdHours"
# StockOptionLevel shortened to StockOption
colnames(Employee_rawdata)[28] <- "StockOption"
# TotalWorkingYears shortened to NumWorkYear
colnames(Employee_rawdata)[29] <- "NumWorkYear"
# TrainingTimesLastYear shortened to TrainTime
colnames(Employee_rawdata)[30] <- "TrainTime"
# WorkLifeBalance shortened to WorkLifeBal
colnames(Employee_rawdata)[31] <- "WorkLifeBal"
# YearsAtCompany shortened to YearsAtCo
colnames(Employee_rawdata)[32] <- "YearsAtCo"
# YearsInCurrentRole shortened to DuraCurRole
colnames(Employee_rawdata)[33] <- "DuraCurRole"
# YearsSinceLastPromotion shortned to LastPromote
colnames(Employee_rawdata)[34] <- "LastPromote"
# YearsWithCurrManager shortened to CurManage
colnames(Employee_rawdata)[35] <- "CurManage"
str(Employee_rawdata)
```

### General Information
``` {r tables}
mytable_performance<- xtabs(~PerformRate+Attrition, data=Employee_rawdata)
round(prop.table(mytable_performance,1)*100,2)
mytable_age<- xtabs(~Age+Attrition, data=Employee_rawdata)
round(prop.table(mytable_age,1)*100,2)
mytable_overtime<- xtabs(~OverTime+Attrition, data=Employee_rawdata)
round(prop.table(mytable_overtime,1)*100,2)
mytable_worklifebalance<- xtabs(~WorkLifeBal+Attrition, data=Employee_rawdata)
round(prop.table(mytable_worklifebalance,1)*100,2)
mytable_jobrole<- xtabs(~JobRole+Attrition, data=Employee_rawdata)
round(prop.table(mytable_jobrole,1)*100,2)
mytable_numcompaniesworked<- xtabs(~NumCoWork+Attrition, data=Employee_rawdata)
round(prop.table(mytable_numcompaniesworked,1)*100,2)
mytable_maritalstatus<- xtabs(~MaritalStat+Attrition, data=Employee_rawdata)
round(prop.table(mytable_maritalstatus,1)*100,2)
mytable_gender<- xtabs(~Gender+Attrition, data=Employee_rawdata)
round(prop.table(mytable_gender,1)*100,2)
mytable_environmentsatisfaction<- xtabs(~EnvSatis+Attrition, data=Employee_rawdata)
round(prop.table(mytable_environmentsatisfaction,1)*100,2)
mytable_businesstravel<- xtabs(~Travel+Attrition, data=Employee_rawdata)
round(prop.table(mytable_businesstravel,1)*100,2)
mytable_educationfield<- xtabs(~EduField+Attrition, data=Employee_rawdata)
round(prop.table(mytable_educationfield,1)*100,2)
mytable_jobsatisfaction<- xtabs(~JobSatis+Attrition, data=Employee_rawdata)
round(prop.table(mytable_jobsatisfaction,1)*100,2)
mytable_education<- xtabs(~Education+Attrition, data=Employee_rawdata)
round(prop.table(mytable_education,1)*100,2)
mytable_jobinvolvement<- xtabs(~JobInvolve+Attrition, data=Employee_rawdata)
round(prop.table(mytable_jobinvolvement,1)*100,2)
mytable_salaryincrease<- xtabs(~SalaryIncr+Attrition, data=Employee_rawdata)
round(prop.table(mytable_salaryincrease,1)*100,2)
mytable_trainingtime<- xtabs(~TrainTime+Attrition, data=Employee_rawdata)
round(prop.table(mytable_trainingtime,1)*100,2)
mytable_yearsatcompany<- xtabs(~YearsAtCo+Attrition, data=Employee_rawdata)
round(prop.table(mytable_yearsatcompany,1)*100,2)
mytable_yearsincurrentrole<- xtabs(~DuraCurRole+Attrition, data=Employee_rawdata)
round(prop.table(mytable_yearsincurrentrole,1)*100,2)
mytable_lastpromotion<- xtabs(~LastPromote+Attrition, data=Employee_rawdata)
round(prop.table(mytable_lastpromotion,1)*100,2)
mytable_yearswithmanager<- xtabs(~CurManage+Attrition, data=Employee_rawdata)
round(prop.table(mytable_yearswithmanager,1)*100,2)
```

### 3A. Prelimary Analysis

``` {r 3a}
# All employees are older than 18
hr <- subset(Employee_rawdata, Employee_rawdata$Age >= 18)
hr$Over18 <- NULL
# All employees had 80 standard work hours
hr$StdHours <- NULL
# All employee counts are 1
hr$EmpCount <- NULL
# Transform Categorical Variables to Indicator Variables
hr <- hr %>% mutate(Attrition=ifelse(Attrition=="Yes", 1, 0))
hr <- hr %>% mutate(Travel=ifelse(Travel=="Travel_Rarely", 2, 
                                                  ifelse(Travel=="Travel_Frequently", 3, 1)))
hr <- hr %>% mutate(Department=ifelse(Department=="Research & Development", 2, 
                                              ifelse(Department=="Sales", 3, 1)))
hr <- hr %>% mutate(EduField=ifelse(EduField=="Life Sciences", 2, 
                                                  ifelse(EduField=="Marketing", 3, 
                                                         ifelse(EduField=="Medical", 4,
                                                                ifelse(EduField=="Other", 5,
                                                                       ifelse(EduField=="Technical Degree", 6, 1))))))
hr <- hr %>% mutate(Gender=ifelse(Gender=="Male", 1, 0))
hr <- hr %>% mutate(JobRole=ifelse(JobRole=="Healthcare Representative", 2,
                                           ifelse(JobRole=="Laboratory Technician", 3,
                                                  ifelse(JobRole=="Manager", 4,
                                                         ifelse(JobRole=="Manufacturing Director", 5,
                                                                ifelse(JobRole=="Research Director", 6, 
                                                                       ifelse(JobRole=="Research Scientist", 7,
                                                                              ifelse(JobRole=="Sales Executive", 8,
                                                                                     ifelse(JobRole=="Sales Representative", 9, 0)))))))))
hr <- hr %>% mutate(MaritalStat=ifelse(MaritalStat=="Married", 2,
                                                 ifelse(MaritalStat=="Divorced", 3, 1)))
hr <- hr %>% mutate(OverTime=ifelse(OverTime=="Yes", 1, 0))
```

### Preliminary Analysis Continued
#### Percent Attriton for JobRole, Department, Business Travel, 
#### Education Field, Years of Education and Marital Status
```{r, echo=T}
# Percent Attrition by Job Role
roles <- Employee_rawdata %>% group_by(JobRole, Attrition) %>% summarise(n = n())
roles[,c("Totals", "Percents")] <- NA
for (x in roles$JobRole)
{
  roles$Totals[roles$JobRole == x] <- sum(Employee_rawdata$JobRole == x)
  roles$Percents[roles$JobRole == x] <- roles$n[roles$JobRole == x] / roles$Totals[roles$JobRole == x] * 100
}
roles <- as.data.frame(roles)
# Percent Attrition by Department
depts <- Employee_rawdata %>% group_by(Department, Attrition) %>% summarise(n = n())
depts[,c("Totals", "Percents")] <- NA
for (x in depts$Department)
{
  depts$Totals[depts$Department == x] <- sum(Employee_rawdata$Department == x)
  depts$Percents[depts$Department == x] <- depts$n[depts$Department == x] / depts$Totals[depts$Department == x] * 100
}
depts <- as.data.frame(depts)
# Percent Attrition by Travel
travel <- Employee_rawdata %>% group_by(Travel, Attrition) %>% summarise(n = n())
travel[,c("Totals", "Percents")] <- NA
for (x in travel$Travel)
{
  travel$Totals[travel$Travel == x] <- sum(Employee_rawdata$Travel == x )
  travel$Percents[travel$Travel == x] <- travel$n[travel$Travel == x] / travel$Totals[travel$Travel == x] * 100
}
travel <- as.data.frame(travel)
# Percent Attrition by Education Field
educfield <- Employee_rawdata %>% group_by(EduField, Attrition) %>% summarise(n = n())
educfield[,c("Totals", "Percents")] <- NA
for (x in educfield$EduField)
{
  educfield$Totals[educfield$EduField == x] <- sum(Employee_rawdata$EduField == x)
  educfield$Percents[educfield$EduField == x] <- educfield$n[educfield$EduField == x] / educfield$Totals[educfield$EduField == x] * 100
}
educfield <- as.data.frame(educfield)
# Percent Attrition by Gender
gender <- Employee_rawdata %>% group_by(Gender, Attrition) %>% summarise(n = n())
gender[,c("Totals", "Percents")] <- NA
for (x in gender$Gender)
{
  gender$Totals[gender$Gender == x] <- sum(Employee_rawdata$Gender == x)
  gender$Percents[gender$Gender == x] <- gender$n[gender$Gender == x] / gender$Totals[gender$Gender == x] * 100
}
gender <- as.data.frame(gender)
# Percent Attrition by Years of Education
educyr <- Employee_rawdata %>% group_by(Education, Attrition) %>% summarise(n = n())
educyr[,c("Totals", "Percents")] <- NA
for (x in educyr$Education)
{
  educyr$Totals[educyr$Education == x] <- sum(Employee_rawdata$Education == x)
  educyr$Percents[educyr$Education == x] <- educyr$n[educyr$Education == x] / educyr$Totals[educyr$Education == x] * 100
}
educyr <- as.data.frame(educyr)
# Percent Attrition by Marital Status
marital_status <- Employee_rawdata %>% group_by(MaritalStat, Attrition) %>% summarise(n = n())
marital_status[,c("Totals", "Percents")] <- NA
for (x in marital_status$MaritalStat)
{
  marital_status$Totals[marital_status$MaritalStat == x] <- sum(Employee_rawdata$MaritalStat == x)
  marital_status$Percents[marital_status$MaritalStat == x] <- marital_status$n[marital_status$MaritalStat == x] / marital_status$Totals[marital_status$MaritalStat == x] * 100
}
marital_status <- as.data.frame(marital_status)
```

#### Correlation Plot of all variables
```{r, echo=TRUE, fig.height=8, fig.width=8}
# Build Correlation Plot
hrCorr <- cor(hr)
colnames(hrCorr) <- c("Age", "Attrition", "Business Travel", "Daily Rate", "Department", "Distance From Home", "Education", "Education Field", "Employee Number", "Environment Satisfaction", "Gender", "Hourly Rate", "Job Involvement", "Job Level", "Job Role", "Job Satisfaction", "Marital Status", "Monthly Income", "Monthly Rate", "Number of Companies Worked", "OverTime", "Percent Salary Hike", "Performance Rating", "Relationship Satisfaction", "Stock Option Level", "Total Working Years", "Training Times Last Year", "Work Life Balance", "Years At Company", "Years In Current Role", "Years Since Last Promotion", "Years With Current Manager")
rownames(hrCorr) <- c("Age", "Attrition", "Business Travel", "Daily Rate", "Department", "Distance From Home", "Education", "Education Field", "Employee Number", "Environment Satisfaction", "Gender", "Hourly Rate", "Job Involvement", "Job Level", "Job Role", "Job Satisfaction", "Marital Status", "Monthly Income", "Monthly Rate", "Number of Companies Worked", "OverTime", "Percent Salary Hike", "Performance Rating", "Relationship Satisfaction", "Stock Option Level", "Total Working Years", "Training Times Last Year", "Work Life Balance", "Years At Company", "Years In Current Role", "Years Since Last Promotion", "Years With Current Manager")
corrplot(hrCorr, method = 'color', number.cex = 0.65, tl.cex = 0.70, type = 'full', title = "Correlation Plot of all Variables", mar=c(0,0,2,0), diag=FALSE)
```

### 3B

``` {r 3b}
require(pastecs)
# Consider Department, EducationBackground, JobRole, and Gender with Credentials
Credentials <- hr[,(names(hr) %in%
                                   c("Age","Education","JobLevel","PerformRate"))]
                                 
# Consider Marital Status with Satisfaction
LifeSatisfaction <- hr[,(names(hr) %in%
                                  c("DisFromHome","EnvSatis","JobInvolve","JobSatis","RelateSatis","WorkLifeBal"))]
                              
# Consider Overtime with Compensation                                  
Compensation <- hr[,(names(hr) %in%
                                  c("DailyRate","HourlyRate","MonthlyRate","MonIncome","SalaryIncr","LastPromote","StockOption"))]
Loyalty <- hr[,(names(hr) %in%
                             c("NumComWork","NumWorkYear","YearsAtCo","DuraCurRole","CurManage"))]
stat.desc(Credentials)
stat.desc(LifeSatisfaction)
stat.desc(Compensation)
stat.desc(Loyalty)
require(ggplot2)
# Histogram of Employee Monthly Incomes
ggplot(hr, aes(x=MonIncome)) + geom_histogram(color="black", fill="white",bins = 25) + 
  labs(title = "Histogram of Monthly Income", x = "Monthly Income", y = "Frequency") + 
  theme(plot.title = element_text(hjust = 0.5))
# Histogram of Percent Salary Hikes
ggplot(hr, aes(x=SalaryIncr)) + geom_histogram(color="black", fill="white",bins=4) + 
  labs(title = "Histogram of Percent Salary Hike", x = "Percent Salary Hike", y = "Frequency") + 
  theme(plot.title = element_text(hjust = 0.5))
```

* The histogram for Employee Monthly Income has a distribution skewed to the right with a long-tail. This makes sense because a few executive position salaries will skew the distribution heavily to the right because they demand salaries greater than the company average.
* The histogram for Percent Salary Hike in Employee salaries has a nearly normal distribution, but exhibits a slight right-skew.

### 3C

``` {r 3c}
# Frequency Table for Employee Gender
Gender <- as.data.frame(table(Employee_rawdata$Gender))
colnames(Gender) <- c("Gender","Frequency")
Gender
# Frequency Table for Employee Education
Education <- as.data.frame(table(Employee_rawdata$EduField))
colnames(Education) <- c("Education","Frequency")
Education
# Frequency Table for Employee Occupation
Occupation <- as.data.frame(table(Employee_rawdata$JobRole))
colnames(Occupation) <- c("Occupation","Frequency")
Occupation
```

### 3D

```{r 3d}
# Frequency table of Management Positions
Management <- Occupation[c(4:6),]
colnames(Management) <- c("Position","Frequency")
Management
```

``` {r EDA}
# Labeling Income Level by Annual Salary
for (i in 1:nrow(hr)) {
  if (hr$MonIncome[i] < 2500){ # <30k annually
    hr$IncomeLvl[i] <- "Entry"
  } else if ((hr$MonIncome[i] >= 2500) & (hr$MonIncome[i] < 4167)){ # 30k - 50k annually
    hr$IncomeLvl[i] <- "Middle"
  } else if ((hr$MonIncome[i] >= 4167) & (hr$MonIncome[i] < 6250)){ # 50k - 75k annually
    hr$IncomeLvl[i] <- "Mid-High"
  } else if ((hr$MonIncome[i] >= 4167) & (hr$MonIncome[i] < 8333)){ # 75k - 100k annually
    hr$IncomeLvl[i] <- "High"
  } else if (hr$MonIncome[i] >= 8333){ # >100k annually
      hr$IncomeLvl[i] <- "Executive"
  }
}
# Table for Attrition by Income Level
xtabs(~IncomeLvl+Attrition, data = hr)
hr_TOcost <- hr[which(hr$Attrition == 1),]
# Approximating Turnover Cost based on CAP Averages
# 20.4% of annual salary used for mid-high and high positions for a conservative estimate
# 125% of annual salary used for executive positions for a conservative estimate
aprxTOcost <- 0
for (i in 1:nrow(hr_TOcost)) {
  if (hr_TOcost$IncomeLvl[i] == "Entry"){
    TOcost <- hr_TOcost$MonIncome[i]*12*0.161
  } else if (hr_TOcost$IncomeLvl[i] == "Middle"){
    TOcost <- hr_TOcost$MonIncome[i]*12*0.197
  } else if (hr_TOcost$IncomeLvl[i] == "Mid-High"){
    TOcost <- hr_TOcost$MonIncome[i]*12*0.204
  } else if (hr_TOcost$IncomeLvl[i] == "High"){
    TOcost <- hr_TOcost$MonIncome[i]*12*0.204
  } else if (hr_TOcost$IncomeLvl[i] == "Executive"){
    TOcost <- hr_TOcost$MonIncome[i]*12*1.25
  }
  aprxTOcost <- aprxTOcost + TOcost
}
aprxTOcost
# Percent Attrition by Years with Current Manager
mytable_curmanage <- xtabs(~CurManage+Attrition, data=Employee_rawdata) 
round(prop.table(mytable_curmanage,1)*100,2) 
# Percent Attrition by Years with Current Manager and Years at Company
mytable_curmanage.yearsatco <- xtabs(~CurManage+YearsAtCo+Attrition, data=Employee_rawdata) 
round(prop.table(mytable_curmanage.yearsatco,1)*100,2) 
# Percet Employy by Number Training Sessions and Job Role
mytable_manager.traintime<- xtabs(~JobRole+TrainTime, data=Employee_rawdata)
round(prop.table(mytable_manager.traintime,1)*100,2)
# Table for Stock Option Income Level
table(hr$IncomeLvl,hr$StockOption)
# Table for Income Level by Job Role
table(Employee_rawdata$JobRole,hr$IncomeLvl)
# Table for Last Promotion by Job Role
table(Employee_rawdata$JobRole,hr$LastPromote)
# Table for Performance Rating by Job Role
table(Employee_rawdata$JobRole,hr$PerformRate)
# Table for Employee Job Satisfaction
table(hr$JobSatis)
```

### 4B

``` {r 4b}
# Percent Attrition by JobRole
roles %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(JobRole, -Percents), y = Percents, fill=JobRole)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Job Role") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Job Role") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Job Role"))
# Percent Attrition by Department
depts %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(Department, -Percents), y = Percents, fill=Department)) + 
  geom_bar(stat = "identity") + 
  xlab("Department") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Department") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Department"))
# Percent Attrition by Travel
travel %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(Travel, -Percents), y = Percents, fill=Travel)) + 
  geom_bar(stat = "identity") + 
  xlab("Business Travel") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Business Travel") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Business Travel"))
# Percent Attrition by Education Field
educfield %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(EduField, -Percents), y = Percents, fill=EduField)) + 
  geom_bar(stat = "identity") + 
  xlab("Education Field") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Field of Education") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Education Field"))
# Percent Attrition by Gender
gender %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(Gender, -Percents), y = Percents, fill=Gender)) + 
  geom_bar(stat = "identity") + 
  xlab("Gender") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Gender") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Gender"))
# Percent Attrition by Years of Education
educyr %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(Education, -Percents), y = Percents, fill=Education)) + 
  geom_bar(stat = "identity") + 
  xlab("Years of Education") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Years of Education") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Years of Education"))
# Percent Attrition by Marital Status
marital_status %>% filter(Attrition == "Yes") %>% ggplot(aes(x = reorder(MaritalStat, -Percents), y = Percents, fill=MaritalStat)) + 
  geom_bar(stat = "identity") + 
  xlab("Marital Status") + ylab("Percent Attrition") +
  ggtitle("Percent Attrition by Marital Status") +
  theme_classic() +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  guides(fill=guide_legend(title="Marital Status"))
```

### 4C

``` {r 4c}
ggplot(data=Employee_rawdata,aes(x=Age,y=MonIncome,color=Gender)) + 
            geom_point() + 
            geom_smooth(method = lm, se = FALSE, color = "black") +
            labs(title = "Correlation between Employee Age and Monthly Income", x = "Age (Years)", y = "Monthly Income ($)") +
            theme(plot.title = element_text(hjust = 0.5))
# lm() function fits the Monthly Income and Age variables of the CraftBeers dataset with a linear model using ABV as the response variable and IBU as the explanatory variable
# summary() function produces the result summaries of the linear model fit
# the square root of the R^2 value provides the correlation coefficient for the linear fit model of ABV and IBU
LinearCorrelation <- lm(MonIncome ~ Age, data = hr)
summary(LinearCorrelation)
# R_squared <- 0.2479
Correlation.Age_Income <- sqrt(summary(LinearCorrelation)$r.squared)
Correlation.Age_Income
# unbalanced data - 1233 No vs 237 Yes
Attrition <- as.data.frame(table(hr$Attrition))
colnames(Attrition) <- c("Attrition", "Frequency")
Attrition
```
* There is an apparent relationship between Age and Income. The correlation coefficient of 0.4979 indicates a moderate positive linear correlation between Age and Income.

### 4D

```{r 4d}
fit <- lm(Employee_rawdata$Age ~ Employee_rawdata$JobSatis + Employee_rawdata$RelateSatis + Employee_rawdata$WorkLifeBal )
summary(fit)
pairs(~Employee_rawdata$Age + Employee_rawdata$JobSatis + Employee_rawdata$RelateSatis + Employee_rawdata$WorkLifeBal)
```

* Life Satisfaction -  Summing the Satisfaction variables (Job, Relationship) and Work Life Balance variable to create a Life Satisfaction score.  Comparing separately to Current and Former Employees.   
* Findings -  No correlation of between Age and Life Satisfaction variable were identified.

### Basic Linear Regression
```{r train_test, include=TRUE}
model <- glm(Attrition ~ Age+Travel+Department+DisFromHome+
               Education+EduField+EnvSatis+Gender+JobInvolve+
               JobLevel+JobRole+JobSatis+MaritalStat+MonIncome+NumCoWork+
               OverTime+SalaryIncr+PerformRate+RelateSatis+NumWorkYear+
               TrainTime+WorkLifeBal+YearsAtCo+DuraCurRole+LastPromote+
               CurManage,family=binomial(link='logit'),data=hr)
summary(model)
```

### Decision Tree
```{r, echo=TRUE}

term_vars <- c("Age","Education","MonthlyIncome","BusinessTravel","Department","DistanceFromHome","EducationField", "Gender","JobInvolvement","JobLevel", "JobRole", "JobSatisfaction", "MaritalStatus", "MonthlyIncome","NumCompaniesWorked", "OverTime","PercentSalaryHike","PerformanceRating", "StockOptionLevel", "TotalWorkingYears","TrainingTimesLastYear", "WorkLifeBalance","RelationshipSatisfaction","YearsAtCompany","YearsInCurrentRole", "YearsSinceLastPromotion","YearsWithCurrManager","Attrition")
emp_term_train <- subset(emp, Education < 4)
emp_term_test <- subset(emp, Education >= 4)
set.seed(99)  # set a pre-defined value for the random seed so that results are repeatable
# Decision tree model
rpart_model <- rpart(Attrition ~.,
                     data = emp_term_train[term_vars],
                     method = 'class',
                     parms = list(split='information'),
                     control = rpart.control(usesurrogate = 0,
                                             maxsurrogate = 0))
# Plot the decision tree
rpart.plot(rpart_model, roundint = FALSE, type = 3)
```

### Random Forest Analysis
```{r, echo=TRUE}
emp$resigned <- as.factor(emp$Attrition)  # create factor for Attrition field

emp_cat <- data.frame(emp$Age,emp$Education,emp$MonthlyIncome,emp$BusinessTravel,emp$Department,emp$DistanceFromHome,emp$EducationField, emp$Gender,emp$JobInvolvement,emp$JobLevel, emp$JobRole, emp$JobSatisfaction, emp$MaritalStatus, emp$MonthlyIncome,emp$NumCompaniesWorked, emp$OverTime,emp$PercentSalaryHike,emp$PerformanceRating, emp$StockOptionLevel, emp$TotalWorkingYears,emp$TrainingTimesLastYear, emp$WorkLifeBalance,emp$RelationshipSatisfaction,emp$YearsAtCompany,emp$YearsInCurrentRole, emp$YearsSinceLastPromotion,emp$YearsWithCurrManager,emp$resigned,emp$EmployeeNumber)


col_headings <- c("Age","Education","MonthlyIncome","BusinessTravel","Department","DistanceFromHome","EducationField", "Gender","JobInvolvement","JobLevel", "JobRole", "JobSatisfaction", "MaritalStatus", "MonthlyIncome","NumCompaniesWorked", "OverTime","PercentSalaryHike","PerformanceRating", "StockOptionLevel", "TotalWorkingYears","TrainingTimesLastYear", "WorkLifeBalance","RelationshipSatisfaction","YearsAtCompany","YearsInCurrentRole", "YearsSinceLastPromotion","YearsWithCurrManager","resigned","EmployeeNumber")

names(emp_cat) <- col_headings
emp_train <- subset(emp_cat, Education < 4)
emp_test <- subset(emp_cat, Education >= 4)

emp_train_rose <- ROSE(resigned ~ ., data = emp_train, seed=125)$data
# Tables to show balanced dataset sample sizes

res_vars <- c("Age","Education","BusinessTravel","Department","DistanceFromHome","EducationField", "Gender","JobInvolvement","JobLevel", "JobRole", "JobSatisfaction", "MaritalStatus", "MonthlyIncome","NumCompaniesWorked", "OverTime","PercentSalaryHike","PerformanceRating", "StockOptionLevel", "TotalWorkingYears","TrainingTimesLastYear", "WorkLifeBalance","RelationshipSatisfaction","YearsAtCompany","YearsInCurrentRole", "YearsSinceLastPromotion","YearsWithCurrManager","resigned")
set.seed(222)
emp_res_rose_RF <- randomForest(resigned ~ .,
                           data = emp_train_rose[res_vars],
                           ntree=500, importance = TRUE,
                           na.action = na.omit)
imp <- varImpPlot(emp_res_rose_RF, type=1, n.var = min(20), main="Attrition Variable Importance (Accuracy)", sub = "Random Forest Model", class = NULL, scale=TRUE)
imp <- as.data.frame(imp[1:20,])
imp$varnames <- rownames(imp) # row names to column
rownames(imp) <- NULL  
col_headings <- c("Importance", "varnames")
names(imp) <-col_headings
imp$var_categ <- rep(1:20)


ggplot(imp, aes(x=reorder(varnames, Importance), y=Importance, color=as.factor(var_categ))) + 
  geom_point() +
  geom_segment(aes(x=varnames,xend=varnames,y=0,yend=Importance)) +
  scale_color_discrete(name="Variable Group") +
  ggtitle("Attrition Variable Importance") +
  ylab("Importance Measurement") +
  xlab("Variable Name") +
  theme(legend.position = "none") +
  coord_flip()

```

### Attrition Prediction using Random Forest
```{r, echo=TRUE}
# generate predictions based on test data ("emp_test")
emp_res_rose_RF_pred <- predict(emp_res_rose_RF, newdata = emp_test)
confusionMatrix(data = emp_res_rose_RF_pred,
                reference = emp_test$resigned,
                positive = "Yes", mode = "prec_recall")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r, echo=TRUE}

# Calculate prediction probabilites of employees who will resign
emp_res_rose_RF_pred_probs <- predict(emp_res_rose_RF, emp_test, type="prob")
Employees_flight_risk <- as.data.frame(cbind(emp_test$EmployeeNumber,emp_res_rose_RF_pred_probs))

# Predition table formatting using kable

col_headings <- c("Employee Num","No","Yes")
names(Employees_flight_risk) <- col_headings
Employees_flight_risk <- arrange(Employees_flight_risk, desc(Yes))
Employees_flight_risk[1:25, 1 ] <- "####"
write.csv(Employees_flight_risk[1:25, ], file = "Data/FlightRiskData.csv")
Employees_flight_risk[1:25, 3]  <- paste(round((Employees_flight_risk[1:25, 3])*100,digits=0),"%",sep="")
Employees_flight_risk[, 2]  <- NULL
c1 <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20)
df <- data.frame(c1, Employees_flight_risk[1:20, 1 ], Employees_flight_risk[1:20, 2])
col_headings <- c("#", "Employee Number","Predict Attrition %")
names(df) <- col_headings
kable(df, caption="Attrition Prediction Table") %>%
  kable_styling(bootstrap_options = "striped", font_size = 11)

```

# Conclusion

Data analysis indicates that DDSAnalytics has higher attrition rates among younger people, which according to SHRM (the Society of Human Resource Management) is more common among that demographic in part due to the low unemployment rate in the current economy which makes it a job seeker's market. Another reason younger people may leave jobs is simply because as a demographic, younger people tend to continuously seek better employment opportunities.
Data analysis indicates that DDSAnalytics also has somewhat high attrition rates among employees with fewer years at the company. This is in line with the industry, and an effective way to curb this is to tweak the company's recruitment process and improve onboarding procedures. Ensuring potential hires have realistic expectations of the company and a good understanding of DDSAnalytics' corporate culture, and helping them develop loyalty to the company through an immersive onboarding process are two ways to reduce attrition for employees with less than two years of service with the company.
Finally, data analysis indicates that overall employee satisfaction with their job and the work environment, feeling involved in their job role, and a good work/life balance all have a significant impact on overall attrition. DDSAnalytics can reduce attrition rates resulting from these factors by introducing a flexible work schedule, involving employees in relevant decisionmaking processes, and reconfiguring the amount of overtime and/or business travel required.


